A Standardized Effect Size for Evaluating and Comparing the Strength of Phylogenetic Signal

### 2020-07-17 Manuscript/PNAS-Adams-01.tex

\author[a,1]{Dean C. Adams}
\author[a,b]{Erica K. Baken}
\author[b]{Michael L. Collyer}

@@

\textsuperscript{1}To whom correspondence should be addressed. E-mail:
\href{mailto:dcadams@iastate.edu}{\nolinkurl{dcadams@iastate.edu}}}

@@

\begin{figure}
\centering
\includegraphics{new.fig.3.temp.png}
\caption{Response of effect sizes \(Z_\lambda\) and \(Z_\kappa\) to
increasing strength of Brownian motion.{}}
\end{figure}

>>>>

\author[a,2]{Dean C. Adams}
\author[a,b]{Erica K. Baken}
\author[b]{Michael L. Collyer}

@@

\textsuperscript{2}To whom correspondence should be addressed. E-mail:
dcadams@iastate.edu}

@@

\begin{figure}
\centering
\includegraphics{new.fig.3.temp.png}
\caption{Response of effect sizes \(Z_{\lambda}\) and \(Z_{\kappa}\) to
increasing strength of Brownian motion.{}}
\end{figure}
